Output Summary

### 2023-04-18 03-post-process/output-plots-children/05-length.Rmd
Reorganize length plots

@@

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )
}

@@

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )

@@

```{r Delta_L_Pb_Mb-1, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,2))
}

```{r Delta_L_Pb_Mb-2, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               Delta_L_Pb_Mb_obs, main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,2))
}

```{r Delta_L_Pb_Mb-3, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # draw the realized time series
  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,2))

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       ylim = range(pred_Delta_L_Pb_Mb_lwr, pred_Delta_L_Pb_Mb_upr, Delta_L_Pb_Mb_lwr, Delta_L_Pb_Mb_upr, na.rm = TRUE),
       xlim = range(L_Pb_seq), 
       main = pops[j]
  )

@@

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       ylim = range(pred_L_Mb_lwr, pred_L_Mb_upr, L_Mb_lwr, L_Mb_upr, na.rm = T),
       xlim = range(L_Pb_seq), 
       main = pops[j]
  )

>>>>

```{r Delta_L_Pb_Mb-1, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,1.6))
}

```{r Delta_L_Pb_Mb-2, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               Delta_L_Pb_Mb_obs, main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,1.6))
}

```{r Delta_L_Pb_Mb-3, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # draw the realized time series
  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,1.6))

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       # ylim = range(pred_Delta_L_Pb_Mb_lwr, pred_Delta_L_Pb_Mb_upr, Delta_L_Pb_Mb_lwr, Delta_L_Pb_Mb_upr, na.rm = TRUE),
       ylim = c(1, 1.6),
       xlim = range(L_Pb_seq), 
       main = pops[j]
  )

@@

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(75,110)
  )
}

@@

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(75,110)
  )

@@

@@

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       # ylim = range(pred_L_Mb_lwr, pred_L_Mb_upr, L_Mb_lwr, L_Mb_upr, na.rm = T),
       ylim = c(75,110),
       xlim = range(L_Pb_seq), 
       main = pops[j]
  )
